---
title: "Homework 2"
author: "Mingee Choi"
date: 10/05/2022
output: github_document
---

Load Packages

```{r setup, message=FALSE}
library(tidyverse)
library(readxl)
library(dplyr)
```

# Problem 2

To import and clean Mr. Trash Wheel and Professor Trash Wheel datasets:

```{r}
mr_trash_wheel_df=
  read_excel("./data/trash.xlsx", sheet=1, range = "A2:N549")%>%
  janitor::clean_names()%>%
  drop_na(data=., dumpster)%>%
  mutate(sports_balls=as.integer(sports_balls))

professor_trash_wheel_df=
  read_excel("./data/trash.xlsx", sheet=2, range = "A2:M96")%>%
  janitor::clean_names()%>%
  drop_na(data=., dumpster)%>%
  mutate(year=as.character(year))
```

To combine two datasets together:

```{r}
mr_trash_wheel_df["trash_wheel_type"] <-"mr_trash_wheel"
professor_trash_wheel_df["trash_wheel_type"] <-"professor_trash_wheel"
trash_df=
   full_join(mr_trash_wheel_df, professor_trash_wheel_df , copy=TRUE)
```

To find key variables
```{r}
round(mean(pull(trash_df, weight_tons), na.rm = TRUE))
round(mean(pull(trash_df, volume_cubic_yards), na.rm = TRUE))
round(mean(pull(trash_df, plastic_bottles), na.rm = TRUE))
```

After including a new variable "Trash Wheel Type", "Mr. Trash Wheel" has 547 observations of 15 variables (547x15) and "Professor Trash Wheel" has 94 observations of 14 variables (94x14). "Mr. Trash Wheel" and "Professor Trash Wheel" have all the same variables except "Professor Trash Wheel" does not have the variable "sport balls". After combining them together by a full join, I get 641 observations of 15 variables (641x15). 

*The combined mean of weight(tons)=3

*The combined mean of volume(cubic yards)=15

*The combined mean of plastic bottles=1958

To find total weight of trash collected by professor trash wheel and the total number of sports balls collected by mr. trash wheel in 2020

```{r}
 sum(pull(professor_trash_wheel_df, weight_tons), na.rm = TRUE)
   filter(mr_trash_wheel_df, year==2020, message=FALSE)
  sum(pull(mr_trash_wheel_df, sports_balls), na.rm = TRUE)
```

Total weight of trash collected by professor trash wheel: 190.12 tons
Total number of sports balls collected by mr. trash wheel in 2020: 6869 sports balls

# Problem 3

Import and clean datasets

```{r}
pols_month_df=
  read_csv("./fivethirtyeight_datasets/pols-month.csv")%>%
  janitor::clean_names()%>%
  separate(mon, into=c("year", "month", "day"))%>%
  mutate(month = month.abb[as.numeric(month)])%>%
  mutate(president = case_when(prez_gop==1 ~"gop", 
                               prez_dem==1 ~"dem")
  )%>%
  mutate(year=as.numeric(year))%>%
  select(-prez_dem,-prez_gop, -day)
  
  
#cleaning second data
snp_df=
   read_csv("./fivethirtyeight_datasets/snp.csv")%>%
   separate(date, into=c("month", "day", "year"))%>% 
   mutate(month = month.abb[as.numeric(month)])%>% 
   mutate(yearfix = case_when(
     year > 20 ~ 1900,
     year < 20 ~ 2000 ))%>% 
   mutate(year = as.numeric(year))%>%
   mutate(year = year + yearfix)%>%
   relocate(year, month)%>%
   select(-day, -yearfix)

#cleaning third data
unemployment_df=
  read_csv("./fivethirtyeight_datasets/unemployment.csv")%>%
  pivot_longer(
    Jan:Dec,
    names_to = "month",
    values_to = "unemployment_percentage")%>%
    janitor::clean_names()%>%
    mutate(year=as.numeric(year))
```                         
 
 Joining datasets by merging snp into pols and merging unemployment into the result
 
 
```{r}
join1_data=
  left_join(pols_month_df, snp_df)
join2_data=
   left_join(join1_data, unemployment_df)                     
```                        

The "pols_month" after cleaning up contains 822 observations of 9 variables (822x9). It contains data from years 1947-2015 and contains the following variables:year, month, gov_gop, sen_gop, rep_gop, gov_dem, sen_dem, and rep_dem. 
The "snp" after cleaning up contains 787 observations of 3 variables (787x3). It contains data from years 1950-2015 and contains the following variables: year, month, and close. 
The "unemployment" after cleaning up contains 641 observations of 15 variables (641x5). It contains data from years 1948-2015 and contains the following variables: year, month, and unemployment percentage. 
The dimension of the combined dataset is 822 observation of 11 variables (822x11). 
                          
                          
                          
 
  






